\documentclass{anstrans}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Demonstration of Demand Driven Deployment Capabilities in \Cyclus}
\author{Gwendolyn J. Chee$^1$, Jin Whan Bae$^1$, Robert R. Flanagan$^2$, Roberto E. Fairhurst$^1$ and Kathryn D. Huff$^1$}

\institute{
$^1$Dept. of Nuclear, Plasma and Radiological Engineering, University of Illinois at Urbana-Champaign \\
$^2$Nuclear Engineering Program, University of South Carolina \\

gchee2@illinois.edu
}

%%%% packages and definitions (optional)
\usepackage{graphicx} % allows inclusion of graphics
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF
\usepackage{xspace}
\usepackage{tabularx}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{placeins}
\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
\newcommand{\SN}{S$_N$}
\renewcommand{\vec}[1]{\bm{#1}} %vector is bold italic
\newcommand{\vd}{\bm{\cdot}} % slightly bold vector dot
\newcommand{\grad}{\vec{\nabla}} % gradient
\newcommand{\ud}{\mathop{}\!\mathrm{d}} % upright derivative symbol
\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%
\newcommand{\Cycamore}{\textsc{Cycamore}\xspace}%
\newcolumntype{c}{>{\hsize=.56\hsize}X}
\newcolumntype{b}{>{\hsize=.7\hsize}X}
\newcolumntype{s}{>{\hsize=.74\hsize}X}
\newcolumntype{f}{>{\hsize=.1\hsize}X}
\newcolumntype{a}{>{\hsize=.45\hsize}X}
\usepackage{titlesec}
\titleformat*{\subsection}{\normalfont}

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Abstract}
\gls{NFC} simulation scenarios are constrained objective functions. 
The objectives are systemic demands such as "1\% power growth", while the 
constraints are availability of new nuclear technology. 
To adequately simulate a nuclear fuel cycle, \gls{NFC} simulators 
must bring demand responsive deployment decisions into the dynamics of the 
simulation logic \cite{huff_current_2017}. 
Thus, a \gls{NFC} simulator should have the capability to deploy 
supporting fuel cycle facilities to meet a user-defined commodity demand. 
While automated power production deployment is common in most fuel cycle 
simulators, automated deployment of supportive fuel cycle 
facilities is non-existent. 
Instead, the user must detail the deployment timeline of all supporting 
facilities or have infinite capacity support facilities. This shortcoming 
exists in the fuel cycle simulator, \Cyclus. 

\Cyclus is an agent-based nuclear fuel cycle simulation framework 
\cite{huff_fundamental_2016}. 
Each entity (i.e. Region, Institution, or Facility) in the fuel cycle is modeled 
as an agent. 
Institution agents
are responsible for deploying and decommissioning facility agents and
can represent a legal operating organization such as a 
utility, government, etc \cite{huff_fundamental_2016}. 

The Demand-Driven \Cycamore Archetype project (NEUP-FY16-10512) aims to 
develop \Cyclus's demand-driven deployment capabilities. 
This capability is developed in the form of a \Cyclus Institution agent that 
deploys facilities to meet the front-end and back-end fuel cycle demands
based on a user-defined commodity demand. 
Its goal is to meet supply for any commodity while minimizing oversupply.
This demand-driven deployment capability is referred to as \texttt{d3ploy}. 

At each time step, \texttt{d3ploy} predicts demand and supply of each commodity for the following time step.
Based on the prediction, \texttt{d3ploy} deploys facilities to 
meet predicted demand. 
The user can select between four types of algorithms to govern demand and supply 
predictions: 
non-optimizing, time series forecasting, deterministic optimizing and machine 
learning. 

We compared the prediction algorithms using numerical experiments that are 
in the form of fuel cycle scenarios in which the
demand driving commodity, its demand curve and the combination of facilities 
in the scenario are varied. 
The types of fuel cycle scenarios studied include front-end facility deployment, 
back-end facility deployment, closed fuel cycle deployment and transition 
scenario deployment scenarios.
We compared the results based on number of time
steps where demand exceeds supply, residuals and $\chi^2$ goodness of fit test.
These comparisons demonstrated that the non-optimizing methods
effectively predicted
appropriate facility deployment for supplying the driving commodity.  
We also found that the time series forecasting, deterministic,
and machine learning 
algorithms were effective for predicting appropriate facility deployment for 
supplying front-end and back-end commodities. The full paper will compare 
these prediction algorithms quantitatively, determine the advantages and 
disadvantages of each and provide recommendations for which algorithm is 
desirable for use in modeling transition scenarios. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{ans}
\bibliography{bibliography}
\end{document}

